
\documentclass[]{csaund_resume-openfont}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated September 17, 2018

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Carolyn}{Saund}{ \urlstyle{same}\href{http://carolynsaund.me}{carolynsaund.me} \\
\href{mailto:carolyn.saund@gmail.com}{carolyn.saund@gmail.com} | +44.759.557.9616
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.30\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{MSc Research Methods in Psychology}
\descript{University of Glasgow | Glasgow, UK}
\location{September 2019 (Expected)}
\sectionsep

\subsection{BSc Computer Science, Brain and Cognitive Science}
\descript{Tufts University | Somerville MA, USA}
\descript{University of Canterbury | Christchurch, NZ}
\location{May 2015}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Advanced Topics in Machine Learning \\
Computational Models of Cognitive Science \\
Stochastic Systems \\
Linear Algebra \\
Machine Architecture and Assembly \\
Advanced Topics in Artificial Intelligence \\
\sectionsep

\subsection{Continuing}
Advanced Seminar in Cognitive Architectures \\
Neural Networks for Machine Learning 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
\location{Fluent:}
Javascript \textbullet{} Python \textbullet{} C \\
C++ \textbullet{} Java \textbullet{} R   \\
\location{Familiar:}
LISP \textbullet{} CSS \textbullet{} HTTP \textbullet{} Go \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space

\subsection{Workflow/Frameworks}
git/github \textbullet{} NodeJS  \textbullet{} React \textbullet{} SVN \textbullet{}  Unix/Linux \textbullet{} Jenkins/TDD \textbullet{} CI releases \textbullet{}
 Stash \textbullet{} Phabricator/arcanist \textbullet{} Gradle
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Public Speaking and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{Msc, Research Methods in Psychological Science} \\
\location{Sept 2018 - Sept 2019 (Expected) | University of Glasgow}
\location{Supervisors: Philippe Schyns \& Stacy Marsella}
\vspace{\topsep} % Hacky fix for vert space
\begin{tightemize}
\item Design and implemenation of bodily gesture system for virtual humans to compare naturalness of accompanying speech patterns and consequential efficacy of communication.
\item MEG analysis of motion data when making semantic decisions on gestures for use in determining information integration areas in the adult human brain.
\end{tightemize}
\sectionsep
\runsubsection{Method and Technique Proficiencies}
\location{}
\begin{tightemize}
\item Fluency in statistical processing using R, SciPy, and Pandas
\item Familiarity with deep learning libraries and implementation techniques, including TensorFlow, Theano, Hadoop
\item Trained in MEG and fMRI imaging techniques
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}
\runsubsection{Cogito} 

\descript{Platform Team Lead}
\location{Jan 2018 - August 2018 | Boston MA}
\begin{tightemize}
\item Managed Agile team of 10 engineers 
\item Oversaw top-to-bottom implementation of three major user-facing features
\end{tightemize}

\descript{Senior Software Engineer }
\location{August 2017 - Jan 2018 | Boston MA}
\begin{tightemize}
\item Originally Implemented and manage release pipeline.
\item Full-stack development of Role-Based User Management (RBUM) APIs.
\end{tightemize}
\sectionsep

\runsubsection{Jibo} \\
\descript{Character AI Engineer }
\location{Jan 2017 - August 2017 | Boston, MA}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed and implemented robotic bi-axial Emotion System and corresponding impacts on robot behavior.
\item Single-handedly architected and maintained robot listening pipeline (main interface for interaction).
\end{tightemize}
\descript{Robot SDK Engineer }
\location{May 2015 - Dec 2016 | Boston, MA}
\begin{tightemize}
\item Architected data APIs for dev tools to manage robot sensory input from cameras and microphones.
\item Implemented frontend UI and developer interfaces to build high-level skills.
\end{tightemize}
\descript{ Software Consultant }
\location{August 2017 - December 2017 | Boston, MA}
\sectionsep

\runsubsection{Spotify} \\
\descript{Software Engineering Intern }
\location{May 2014 - Sep 2014 | NY, NY}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full stack development of internal desktop application.
\item Developed web APIs and GUI for music annotation tools
\end{tightemize}
\sectionsep

\end{minipage}

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Other Extracurriculars and Awards
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Talks \& Memberships}
\runsubsection{Conferences and Presentations}
\descript {}
\begin{tightemize}
\item Women Engineers Code - Abstraction and API Design
\item Women in Technology - Imposter Syndrome
\item Lesbians Who Tech - Presentation on emotional future of robotics 
\item Boston ML Meetup - Human-Computer Interfaces
\item Tufts WICS Conference, Alumni Pannel 
\end{tightemize}
\sectionsep

\runsubsection{Workshops}
\descript {}
\begin{tightemize}
\item SXSW - Getting started with social robots
\item MLHacks - Jibo SDK \& App design for social robots
\end{tightemize}
\sectionsep

\runsubsection{Memberships \& Activities}
\descript{ }
\begin{tightemize}
\item Cognitive Science Society
\item Biologically Inspired Cognitive Architectures Society
\item British Psychological Society
\item British Computing Society
\item University of Glasgow Robotics Society
\item University of Glasgow FemEng Society
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Community Service
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership and Community Service}

\runsubsection{University of Glasgow Psychology Department}
\descript{| Athena SWAN Committee Member}
\location{Oct 2018 - Present | Glasgow, UK}
\begin{tightemize}
\item On Student committee for department Athena SWAN chapter.
\item Designed and implemented initiatives to encourage students to become STEM Ambassadors.
\item Implemented metric gathering mechanism to track demographics of seminar and workshop participation.
\item Collaborated with sociology department on evaluation metrics and surveys to ensure validity of efficacy reports.\end{tightemize}
\sectionsep

\runsubsection{University of Glasgow Psychology Department}
\descript{| Student Representative Council}
\location{Sept 2018 - Present | Glasgow, UK}
\begin{tightemize}
\item Gathered feedback on courses, program structure, and student experience.
\item Participated in Student Council meetings to represent program cohort.
\item Collaborated with faculty and staff on program and messaging improvements.
\end{tightemize}
\sectionsep

\runsubsection{Tufts University Computer Science Department}
\descript{| Women In Computer Science President}
\location{Jan 2013 - Jan 2015 | Somerville, MA}
\begin{tightemize}
\item Coordinated logistics of club hackathons, speakers, and outreach.
\item Led executive board in creating WiCS mission and club constitution.
\end{tightemize}
\sectionsep

\runsubsection{STEM Ambassadors}
\descript{| Volunteer}
\location{Oct 2018 - Present | Glasgow, UK}
\begin{tightemize}
\item Participate in career talks and robotics demos for high schoolers.
\item Facilitate and mentor high school robotics team.
\end{tightemize}
\sectionsep

\runsubsection{Girl Guiding}
\descript{| Volunteer}
\location{Sept 2018 - Present | Glasgow, UK}
\begin{tightemize}
\item Volunteer weekly with troupe leading leadership and cooperation building skills.
\item Supervise weekend trips to museums and venues around Glasgow.
\end{tightemize}
\sectionsep

\runsubsection{Cambridge Inventors Club}
\descript{| Organizer \& Co-Coordinator }
\location{Jan 2016 - June 2018 | Cambridge, MA}
\begin{tightemize}
\item Worked with children age 8-13 on engineering fundamentals, such as iterative design, retrospectives, and cooperation
\end{tightemize}
\sectionsep

\runsubsection{Girls Who Code}
\descript{| Instructor}
\location{Sept 2015 - June 2016 | Belmont, MA}
\begin{tightemize}
\item Instructed three levels of middle- and high-school aged students from introduction to basic data strcutures. 
\item Supplemented given course materials with additional lesson plans to emphasize CS fundamentals.
\end{tightemize}
\sectionsep


\end{document}  \documentclass[]{article}
